基于卷积神经网络的视觉目标跟踪算法研究

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{Many thanks for your positive comments on the strength of our paper and the novelty of the proposed attack method.}

%%%% 问题 1.1 %%%%
\textit{In addition, I suggest the authors add more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. The experimental results show that it is effective to use the predicted boxes instead of ground truth boxes for training perturbations.}

\textbf{Thanks for the good comment. As suggessted, we have added more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. Specifically, we evaluate the untargeted and targeted attack performance on the following datasets and metrics: (1) AO and precision on OTB2015, (2) SR and AO on GOT-Val, and (3) precision, normalized precision and AO on LaSOT.
% 新增加的实验结果分析位于某处，展示如下。
The detailed analysis of new added experiments is added in Section IV.D of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

\begin{table}[t]
  \renewcommand\thetable{VII}
  \centering
  \caption{Attack results on OTB2015, GOT-Val and LaSOT with or without the ground truth information. w/ GT represents that we train perturbations using the groud truth bounding box information of the trainig dataset. w/o GT represents that we train perturbations using the predicted boxes instead of ground truth boxes of the training dataset.}
  \begin{tabular}{rrcccc}
  \toprule
  \multirow{2}{*}[-2pt]{Benchmarks} & \multirow{2}{*}[-2pt]{Metrics} & \multicolumn{2}{c}{Unargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
                              &                          & w/ GT  & \multicolumn{1}{l}{w/o GT}  & w/ GT  & \multicolumn{1}{l}{w/o GT} \\ \midrule
  \multirow{2}{*}{OTB2015}     & AO                       & 0.063  & 0.056                       & 0.759  & 0.752                      \\
                              & Precision                & 0.092  & 0.080                       & 0.795  & 0.794                      \\ \midrule
  \multirow{2}{*}{GOT-Val}    & SR                       & 0.123  & 0.121                       & 0.890  & 0.893                      \\
                              & AO                       & 0.153  & 0.160                       & 0.840  & 0.833                      \\ \midrule
  \multirow{3}{*}{LaSOT}      & Precision                & 0.046  & 0.043                       & 0.605  & 0.531                      \\
                              & Norm. Prec.              & 0.048  & 0.044                       & 0.702  & 0.660                      \\
                              & AO                       & 0.069  & 0.063                       & 0.691  & 0.646                      \\ \bottomrule
  \end{tabular}
  \label{tab:agent_GT}
\end{table}

\uline{We evaluate the untargeted and targeted attack performance on the following datasets and metrics: (1) AO and precision on OTB2015, (2) SR and AO on GOT-Val, and (3) precision, normalized precision and AO on LaSOT.
Experimental results are shown in Table \ref{tab:agent_GT}.
In terms of AO on GOT-Val, the untargeted attack performance is 0.153 when the ground truth is used to train perturbations and 0.160 when the ground truth is not used.
In terms of the precision score on OTB2015, the targeted attack performance is 0.795 when the ground truth is used to train perturbations and 0.794 when the ground truth is not used.
In terms of the normalized precision score on LaSOT, the targeted attack performance is 0.702 when the ground truth is used to train perturbations and 0.660 when the ground truth is not used.
Therefore, it is effective to use the predicted boxes instead of ground truth boxes for training perturbations.
}

### 2021-09-27 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
了改的
的改个
串联改串接。漏字：个。

总体而言，本章提出了空间信息增强的视觉目标跟踪算法具有如下特点：
\begin{itemize}
\item 使用整个图像而不是小的图像块作为跟踪器的输入，以为跟踪器提供更丰富的全局空间信息。
\item 为了更好地感知全局空间信息，本章提出了一个两阶段跟踪框架，该框架能够检测在视觉表观上类似于真实目标的候选目标区域。
\item 为了消除候选目标区域中近似物体的干扰，本章提出了一个轨迹预测模块，该模块能够通过预测目标在当前帧的位置分布以排除近似物体，获得最终的跟踪结果。
\end{itemize}

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region.
在第二阶段，对融合特征 $f_{corr}$ 执行 RoI Align 操作，为每个 RoI 生成一个小特征图，其通道尺寸为 2048，空间分辨率固定为 7 $\times$ 7：
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
其中 $b_{roi}^{i}$ 是候选区域 $i$ 的边界框。
最后，每个 RoI 被分类为前景或背景。在测试期间，我们选择排名靠前的 $K$ 的 RoI 作为候选目标，这些目标将在轨迹预测模块中进行后处理。

@@

令 $H_{t}^{k} = \{h_{t-i}\}_{i=1:k}$ 表示历史轨迹信息，其中 $t$ 是当前帧的索引，$k$ 是历史长度，$h_{j} = \{x_{j}, y_{j}\}$ 是一个二维坐标，表示目标在帧 $j$ 中的位置。
受姿态估计任务的启发，我们将 $h_{j}$ 表示为二维高斯热图 $m_{j} \in \mathbb R^{h \times w}$，其中二维高斯顶点位于目标位置 $(x_{j}, y_{j})$。
为了对目标的轨迹信息进行建模，我们根据时间顺序将生成的 $k$ 热图进行串接，以获得通道维度为 $k$ 的轨迹张量 $\mathcal{M} \in \mathbb{R}^{k \times h \times w}$：
\begin{equation}
    \mathcal{M}_{t}^{k} = \mathcal{C}(m_{t-k}, m_{t-k+1}, ..., m_{t-1}),
\end{equation}
其中 $\mathcal{C}(\cdot)$ 表示串联操作。

>>>>

总体而言，本章提出的空间信息增强的视觉目标跟踪算法具有如下特点：
\begin{itemize}
\item 使用整个图像而不是小的图像块作为跟踪器的输入，以为跟踪器提供更丰富的全局空间信息。
\item 为了更好地感知全局空间信息，本章提出了一个两阶段跟踪框架，该框架能够检测在视觉表观上类似于真实目标的候选目标区域。
\item 为了消除候选目标区域中近似物体的干扰，本章提出了一个轨迹预测模块，该模块能够通过预测目标在当前帧的位置分布以排除近似物体，获得最终的跟踪结果。
\end{itemize}

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region.
在第二阶段，对融合特征 $f_{corr}$ 执行 RoI Align 操作，为每个 RoI 生成一个小特征图，其通道尺寸为 2048，空间分辨率固定为 7 $\times$ 7：
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
其中 $b_{roi}^{i}$ 是候选区域 $i$ 的边界框。
最后，每个 RoI 被分类为前景或背景。在测试期间，我们选择排名靠前的 $K$ 个 RoI 作为候选目标，这些目标将在轨迹预测模块中进行后处理。

@@

令 $H_{t}^{k} = \{h_{t-i}\}_{i=1:k}$ 表示历史轨迹信息，其中 $t$ 是当前帧的索引，$k$ 是历史长度，$h_{j} = \{x_{j}, y_{j}\}$ 是一个二维坐标，表示目标在帧 $j$ 中的位置。
受姿态估计任务的启发，我们将 $h_{j}$ 表示为二维高斯热图 $m_{j} \in \mathbb R^{h \times w}$，其中二维高斯顶点位于目标位置 $(x_{j}, y_{j})$。
为了对目标的轨迹信息进行建模，我们根据时间顺序将生成的 $k$ 个热图进行串接，以获得通道维度为 $k$ 的轨迹张量 $\mathcal{M} \in \mathbb{R}^{k \times h \times w}$：
\begin{equation}
    \mathcal{M}_{t}^{k} = \mathcal{C}(m_{t-k}, m_{t-k+1}, ..., m_{t-1}),
\end{equation}
其中 $\mathcal{C}(\cdot)$ 表示串接操作。
